### 2020-04-29 README.Rmd
Add results for Bristol, heads-up @joeytalbot

```{r, include = FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(sf)
library(tmap)
tmap_mode("view")
piggyback::pb_download("las_top.Rds")
las_top = readRDS("las_top.Rds")
rsf = readRDS("rsf_grouped_long.Rds")
# piggyback::pb_download("rsf.Rds", "cyipt/cyipt-phase-1-data")
```

```{r, eval=FALSE}
# general analysis of data
rsf = readRDS("rsf.Rds")
names(rsf)
rtid = readr::read_csv("~/cyipt/cyipt-server-data/malcolm/roadtypes.csv")
rsf = left_join(rsf, rtid)
rsf_spare_lane = rsf %>% filter(
  (lanespsvforward + lanesforward) > 1 |
  (lanespsvbackward + lanesbackward) > 1,
  ! grepl(pattern = "motorway", highway)
  ) 
saveRDS(rsf_spare_lane, "rsf_spare_line.Rds")
# piggyback::pb_upload("rsf_spare_line.Rds", "cyipt/cyipt-phase-1-data")

@@

rsf_grouped$length = sf::st_length(rsf_grouped) %>% as.numeric()
summary(rsf_grouped$length)
rsf_grouped_long = rsf_grouped %>% filter(length > 100)
# mapview::mapview(rsf_grouped_long)
rsf_grouped_long %>%
  st_drop_geometry() %>% 
  arrange(desc(pctgov)) %>%
  group_by(region) %>% 
  slice(1:10) 
tm_shape(rsf_grouped_long) + tm_lines("pctgov", lwd = 3, palette = "viridis")  
saveRDS(rsf_grouped_long, "rsf_grouped_long.Rds")
```

@@

```{r}
roads = rsf %>% filter(region == "Cambridge", pctgov > 400)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_view(set.zoom.limits = c(13, 14)) + tm_scale_bar()
```

@@

```{r}
roads_top = roads %>%
  filter(length > 100) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(14, 15)) + tm_scale_bar()

@@

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE,
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(sf)
library(tmap)
tmap_mode("view")
# piggyback::pb_download("las_top.Rds")
pct_las = sf::read_sf("https://github.com/cyipt/tempCycleways/releases/download/0.1/pct_la_summaries.geojson")
las_top = readRDS("las_top.Rds")
rsf = readRDS("rsf_grouped_long.Rds")
```

```{r, eval=FALSE}
# general analysis of data
# piggyback::pb_download("rsf.Rds", "cyipt/cyipt-phase-1-data")
rsf = readRDS("rsf.Rds")
names(rsf)
rtid = readr::read_csv("~/cyipt/cyipt-server-data/malcolm/roadtypes.csv")
rsf = left_join(rsf, rtid)
rsf_spare_lane = rsf %>% filter(
  (lanespsvforward + lanesforward) > 1 |
  (lanespsvbackward + lanesbackward) > 1,
  ! grepl(pattern = "motorway", highway)
  ) 
saveRDS(rsf_spare_lane, "rsf_spare_line.Rds")
# piggyback::pb_upload("rsf_spare_line.Rds", "cyipt/cyipt-phase-1-data")

@@

rsf_grouped$length = sf::st_length(rsf_grouped) %>% as.numeric()
summary(rsf_grouped$length)
rsf_grouped_long = rsf_grouped %>% filter(length > 100)
# mapview::mapview(rsf_grouped_long)
rsf_grouped_long %>%
  st_drop_geometry() %>% 
  arrange(desc(pctgov)) %>%
  group_by(region) %>% 
  slice(1:10) 
tm_shape(rsf_grouped_long) + tm_lines("pctgov", lwd = 3, palette = "viridis")  
saveRDS(rsf_grouped_long, "rsf_grouped_long.Rds")
piggyback::pb_upload("rsf_grouped_long.Rds")
```

@@

```{r}
roads = rsf %>% filter(region == "Cambridge", pctgov > 400)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_scale_bar()
```

@@

```{r}
roads_top = roads %>%
  filter(length > 100) %>% 
  arrange(desc(pctgov)) %>%
  slice(1:10) 
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_view(set.zoom.limits = c(14, 150)) + tm_scale_bar()

@@

# Bristol

```{r}
region = pct_las %>% filter(name == "Bristol")
region = sf::st_make_valid(region)
roads = rsf %>% filter(region == "Bristol", pctgov > 100)
roads = roads[region, ]
roads = st_intersection(roads, region)
tm_shape(roads) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_shape(region) + tm_borders() +
  tm_scale_bar() 
```

```{r}
bristol_centre = tmaptools::geocode_OSM("Bristol", as.sf = TRUE)
bristol_buff = stplanr::geo_buffer(bristol_centre, dist = 1500)
roads_top = roads[bristol_buff, ] %>%
  filter(length > 200) %>% 
  arrange(desc(pctgov)) %>%
  slice(2:10) %>% 
  distinct(name, .keep_all = TRUE)
tm_shape(roads_top) + tm_lines("pctgov", lwd = 3, palette = "viridis") +
  tm_text("name") +
  tm_scale_bar()
